Historical trends in the contribution of six major causes of death to the black-white

### 2017-04-25 Manuscript/Manuscript_COD_Trends.Rmd
changes

###Discussion

>>>>

###Discussion 
- the next is to investigate potential state level policy and impact on underlying risk factors
- our analysis highlittghs a few specific causes in a few specific period
-injuries his cvd, not so much on cancer - because there is more homo. across contribution of cancer
- limitations - major groupings but they have lots of heatergeneity of causes within the grouping
- cont of HIV increases very dramatically, but the pace of decline differed - the places where there is a lag in the decline was the more rural places
